Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-07-12 Supplemental-Material-A-Annotated-Analysis.Rmd
three-way anova heading adjusted
S1 scale indices added

<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>

```{r setup, include=FALSE}
# R Studio Clean-Up
cat("\014") # clear console
# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate",
  "purrr",
  "metafor",
  "dygraphs",
  "readxl", 
  "reshape",
  "factoextra"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

@@

--------------------------------------------------------------------

@@

<i class="fas fa-exclamation-circle"></i> Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.

@@

The data were collected using two different survey tools. For the study with sojourners (Study 1: worker) we used the survey platform Qualtrics XM, whereas the studies with international students (Study 2: student), and the international medical professionals (Study 3: medical) were conducted using the survey framework FormR. This means that the datasets had inconsistent file formats and naming conventions. For the Qualtrics study we pre-processed some variables to ease the import process (for the syntax files see the SPS files in '_data/S1_Workers/processed/cleaned_' and for the raw data files see '_data/S1_Workers/raw_'). For the two other studies, we import the raw csv files from their respective folders.

@@

For the sojourner sample data was collected in four separate surveys: (1) the pre-measurement, (2) the daily morning survey, (3) the daily afternoon survey, as well as (4) a post-measurement. We combine the four individual surveys into one cohesive dataframe and drop superfluous variables that are not relevant to the analyses relevant here. We then format the time and date variables and add person- and measurement indices (for easy and meaningful addressing of the data). We also exclude our own test data.  
<i class="fas fa-info-circle"></i> _Note:_ All data preparation steps are saved in the '_dtS1_' list.

@@

For the student sample data was, similarly, collected in three separate surveys: (1) the pre-measurement, (2) the daily survey sent out at lunch and dinner time, and (3) a post-measurement. We combine the three individual surveys into one large dataframe and drop superfluous variables that are not relevant to the analyses relevant here. We exclude our own test data as well as one participant who entered the study twice (but gave different responses during the pre-measurement). We also reformat missing values and format core ID variables.  
<i class="fas fa-info-circle"></i> _Note:_ All data preparation steps are saved in the '_dtS2_' list.

@@

For the medical professionals sample data was, again, collected in three separate surveys: (1) the pre-measurement, (2) the daily survey sent out at lunch and dinner time, and (3) a post-measurement. We combine the three individual surveys into one large dataframe. We exclude our own test data. We also reformat missing values and format core ID variables.  
<i class="fas fa-info-circle"></i> _Note:_ All data preparation steps are saved in the '_dtS3_' list.

@@

1. We first corrected time indicators within the surveys. In some cases participants completed their daily diary surveys for the afternoon after midnight. In these cases the measurement still is in reference to the previous day and is indicated in the corrected variable.   
2. We then created indices of scales. Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).   
3. Finally, we calculated several basic participant summaries (averages across all measurement occasions).

@@

@@

1. We first create person, survey type, and measurement ID variables.   
2. We then created indices of scales. Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).   
3. We add information about the interaction partner to the beep during which a person was selected as an interaction partner.   
4. We cluster mean-center key variables within participants.   
5. Finally, we calculated several basic participant summaries (averages across all measurement occasions).

@@

@@

1. We first create person, survey type, and measurement ID variables.   
2. We then created indices of scales. Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).   
3. We cluster mean-center key variables within participants.   
4. Finally, we calculated several basic participant summaries (averages across all measurement occasions).

@@

<div class="alert alert-info alert-dismissible fade in" role="alert">
  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
  <i class="fas fa-info-circle"></i> <b>Note: </b><br/>
  This needs to be adjusted current missingness criterion set to more conservative 33%.
</div>

@@

```{r testOptimizer05}
cleanM <- function(M, c = 66) {
  check <- list()
  rowNamesOut <- c()
  colNamesOut <- c()
  for (i in 1:length(c(row.names(M), names(M)))) {
    rowMeans <- rowMeans(M) * 100
    colMeans <- colMeans(M) * 100
    rcMeans <- c(rowMeans, colMeans)
    rm <- which.min(rcMeans) %>% names
    rc <- ifelse(startsWith(rm, "PP_"), "row", "col")

@@

dtS1RedInfo <- cleanM(M = as.data.frame(dtS1Availability), c = 66)

@@

```{r s2SampleReduction}
dtS2RedInfo <- cleanM(M = as.data.frame(dtS2Availability), c = 66)

@@

# remove glitch entry 
dtS2Red <- dtS2Red[!(dtS2Red$PID == 46 & dtS2Red$TIDnum == 57 & dtS2Red$ended == "2018-12-20 21:58:31"),]

@@

```{r s3SampleReduction}
dtS3RedInfo <- cleanM(M = as.data.frame(dtS3Availability), c = 66)

@@

We ultimately aim to create 20 imputed datasets to perform the analyses on. As outlined by @Monden2015, we will use the key variables themself as well as auxiliary variables to impute missing values. Auxiliary variables are any pre-, post-, or daily dairy variables other than the main variables. If there are any modeling issues we will limit the auxiliary variables to all variables that that are significantly ($p$ < .01) and meaningfully ($r$ > .3) correlated with (1) the key variables or (2) missingness on the key variables.

We create the imputed data set for each of the analyses. This includes the main analyses with across all three studies, using the set of common variables, as well as follow-up analyses for study-specific, interaction-specific and time scale specific datasets.

```{r varNames}
# varNames
varNamInS123 <- varNames %>%
  filter(
    pca != 0,
    surveyS1 == "daily",
    surveyS2 == "daily",
    surveyS3 == "daily"
  ) %>%
  select(varNam) %>%
  pull
varNamInS1 <- varNames %>%
  filter(
    pca != 0,
    surveyS1 == "daily"
  ) %>%
  select(varNam) %>%
  pull
varNamInS2 <- varNames %>%
  filter(
    pca != 0,
    surveyS2 == "daily"
  ) %>%
  select(varNam) %>%
  pull
varNamInS3 <- varNames %>%
  filter(
    pca != 0,
    surveyS3 == "daily"
  ) %>%
  select(varNam) %>%
  pull
varNamAdd <- c(
  "PID",
  "TID",
  "TIDnum",
  "relatedness",
  "autonomy",
  "competence"
)
varNamOut <- c(
  "ResponseId",
  "relatednessNoInteraction",
  "relatednessSelf",
  "relatednessOther",
  "autonomy_Int",
  "autonomy_NoInt",
  "competence_Int",
  "competence_NoInt",
  varNamInS1[grepl('^MDMQ', varNamInS1)],
  varNamInS2[grepl('^ProSo|^AntiSo', varNamInS2)],
  varNamInS3[grepl(
    '^ProSo|^AntiSo|^agency|^autoFrust|^autoSat|^relatFrust|^relatSat|^compFrust|^compSat|^lonely[0-9]|^emotRegPos|^emotRegNeg',
    varNamInS3
  )]
)
varNamNewS1 <- c(
  "alertness", 
  "calmness", 
  "valence"
)
varNamNewS2 <- c(
  "ProSo", 
  "AntiSo"
)
varNamNewS3 <- c(
  "ProSo", 
  "AntiSo",
  "agency",
  "autoFrust",
  "autoSat",
  "relatFrust",
  "relatSat",
  "compFrust",
  "compSat",
  "lonely",
  "emotRegPos",
  "emotRegNeg"
)
varNamIntDep <- c(
  varNamInS123[grepl('^InteractionContext|AttitudesPartner|KeyNeedDueToPartner|^quality', varNamInS123)]
)

varNamPcaS123 <- c(varNamAdd, varNamInS123[!varNamInS123 %in% varNamOut])
varNamPcaS123Indep <- varNamPcaS123[!varNamPcaS123 %in% varNamIntDep]
varNamPcaS1 <- c(varNamAdd, varNamNewS1, varNamInS1[!varNamInS1 %in% varNamOut])
varNamPcaS2 <- c(varNamAdd, varNamNewS2, varNamInS2[!varNamInS2 %in% varNamOut])
varNamPcaS3 <- c(varNamAdd, varNamNewS3, varNamInS3[!varNamInS3 %in% varNamOut])

@@

```{r MiMain}
library(Amelia)
varNamInMiMain <- varNames %>%
  filter(
    aux == 1,
    studyS1 == "S1",
    studyS2 == "S2",
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull

varNamMiMain <- c(varNamAdd, varNamInMiMain[!varNamInMiMain %in% varNamOut])

varNamInMiMainPsbl <- c(
  paste(varNamMiMain, rep(".pre", length(varNamInMiMain)), sep = ""),
  varNamMiMain,
  paste(varNamMiMain, rep(".post", length(varNamInMiMain)), sep = "")
)

varNamInMiMainRed <- Reduce(
  intersect,
  list(
    dtS1Red %>% select(PID, TID, TIDnum, any_of(varNamInMiMainPsbl)) %>% names,
    dtS2Red %>% select(PID, TID, TIDnum, any_of(varNamInMiMainPsbl)) %>% names,
    dtS3Red %>% select(PID, TID, TIDnum, any_of(varNamInMiMainPsbl)) %>% names
  )
)

@@

```{r MiS1}
varNamInMiS1 <- varNames %>%
  filter(
    aux == 1,
    studyS1 == "S1"
  ) %>%
  select(varNam) %>%
  pull

varNamMiS1 <- c(varNamAdd, varNamInMiS1[!varNamInMiS1 %in% varNamOut])

varNamInMiS1Psbl <- c(
  paste(varNamMiS1, rep(".pre", length(varNamMiS1)), sep = ""),
  varNamMiS1,
  paste(varNamMiS1, rep(".post", length(varNamMiS1)), sep = "")
)

@@

# TO BE ADAPTED:
dtMiS1 <- dtS1Red %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
    ) %>%
  select(
    PID,
    TID,
    TIDnum,
    date,
    week,
    any_of(varNamInMiS1Psbl),
    -time,
    -starts_with("ResponseId")
  ) %>%
  as.data.frame %>%
  mutate_at(vars(-c("TID", "date", "week")), as.numeric) %>%
  select_if(~sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame

#dtS1MiCs <- names(dtMiS1)[endsWith(names(dtMiS1), c(".pre", ".post"))] # cross sectional vars

# MiS1 <-
#   amelia(
#     dtMiS1,
#     m = 1,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars =  c("TID", "date", "week"),
#     #noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     #parallel = "multicore",
#     #ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1, file = "data/imputed/S1Imputed.RData")
# load("data/imputed/S1Imputed.RData")
```

>>>>

```{=html}
<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>
```
```{r setup, include=FALSE}
# R Studio Clean-Up
cat("\014") # clear console
# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate",
  "purrr",
  "metafor",
  "dygraphs",
  "readxl", 
  "reshape",
  "factoextra",
  "Amelia", 
  "ThreeWay"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

@@

------------------------------------------------------------------------

@@

<i class="fas fa-exclamation-circle"></i> Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5\*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.

@@

The data were collected using two different survey tools. For the study with sojourners (Study 1: worker) we used the survey platform Qualtrics XM, whereas the studies with international students (Study 2: student), and the international medical professionals (Study 3: medical) were conducted using the survey framework FormR. This means that the datasets had inconsistent file formats and naming conventions. For the Qualtrics study we pre-processed some variables to ease the import process (for the syntax files see the SPS files in '*data/S1_Workers/processed/cleaned*' and for the raw data files see '*data/S1_Workers/raw*'). For the two other studies, we import the raw csv files from their respective folders.

@@

For the sojourner sample data was collected in four separate surveys: (1) the pre-measurement, (2) the daily morning survey, (3) the daily afternoon survey, as well as (4) a post-measurement. We combine the four individual surveys into one cohesive dataframe and drop superfluous variables that are not relevant to the analyses relevant here. We then format the time and date variables and add person- and measurement indices (for easy and meaningful addressing of the data). We also exclude our own test data.\
<i class="fas fa-info-circle"></i> *Note:* All data preparation steps are saved in the '*dtS1*' list.

@@

For the student sample data was, similarly, collected in three separate surveys: (1) the pre-measurement, (2) the daily survey sent out at lunch and dinner time, and (3) a post-measurement. We combine the three individual surveys into one large dataframe and drop superfluous variables that are not relevant to the analyses relevant here. We exclude our own test data as well as one participant who entered the study twice (but gave different responses during the pre-measurement). We also reformat missing values and format core ID variables.\
<i class="fas fa-info-circle"></i> *Note:* All data preparation steps are saved in the '*dtS2*' list.

@@

For the medical professionals sample data was, again, collected in three separate surveys: (1) the pre-measurement, (2) the daily survey sent out at lunch and dinner time, and (3) a post-measurement. We combine the three individual surveys into one large dataframe. We exclude our own test data. We also reformat missing values and format core ID variables.\
<i class="fas fa-info-circle"></i> *Note:* All data preparation steps are saved in the '*dtS3*' list.

@@

1.  We first corrected time indicators within the surveys. In some cases participants completed their daily diary surveys for the afternoon after midnight. In these cases the measurement still is in reference to the previous day and is indicated in the corrected variable.\
2.  We then created indices of scales. Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).\
3.  Finally, we calculated several basic participant summaries (averages across all measurement occasions).

@@

varNamIndicesS1 <- c(
  "autonomy",
  "competence",
  "relatedness",
  "education_level.pre",
  "associationMerged.pre",
  "assimilation.pre",
  "separation.pre",
  "integration.pre",
  "marginalization.pre",
  "VIA_heritage.pre",
  "VIA_Dutch.pre",
  "SSAS_surrounding.pre",
  "SSAS_privat.pre",
  "SSAS_public.pre",
  "assimilation.post",
  "separation.post",
  "integration.post",
  "marginalization.post",
  "VIA_heritage.post",
  "VIA_Dutch.post",
  "rosenberg.post",
  "social_support.post",
  "stress.post",
  "discrimination.post",
  "discrimination_month.post",
  "NLE_1month.post",
  "NLE_6month.post",
  "NLE_12month.post"
  )

df$roommate.pre_calc <- df %>%
  select(
    starts_with("roommate")
  ) %>% 
  mutate_all(as_factor) %>%
  unite(., "Comb", sep = ", ", remove = TRUE, na.rm = TRUE) %>%
  pull

df$Reason.pre_calc <- df %>%
  select(
    starts_with("Reason"),
    -Reason_nodesire, 
    -ReasonOther.pre 
  ) %>% 
  mutate_all(as_factor) %>% 
  unite(., "Comb", sep = ", ", remove = TRUE, na.rm = TRUE) %>%
  pull

df$occupation.pre_calc <- df %>%
  select(
    starts_with("occupation"),
    -occupation_8_TEXT.pre
  ) %>%
  mutate_all(as_factor) %>% 
  unite(., "Comb", sep = ", ", remove = TRUE, na.rm = TRUE) %>% 
  pull

df$CurrentEducation.pre_calc <-
  df %>%
  select(starts_with("CurrentEducation"),
         -CurrentEducation_6_TEXT.pre) %>%
  mutate_all(as_factor) %>%
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$groupType.pre_calc <-
  df %>%
  select(starts_with("gr_type"),
          -ends_with("TEXT")) %>%
  mutate_all(as_factor) %>% 
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$groupContext.pre_calc <-
  df %>%
  select(starts_with("gr_context"),
          -ends_with("TEXT")) %>%
  mutate_all(as_factor) %>% 
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$dyadType.pre_calc <-
  df %>%
  select(starts_with("dyad_type"),
          -ends_with("TEXT")) %>%
  mutate_all(as_factor) %>% 
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$context.pre_calc <-
  df %>%
  select(starts_with("Context"),
          -ends_with("TEXT")) %>% 
  mutate_all(as_factor) %>% 
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$desireType.pre_calc <-
  df %>%
  select(starts_with("desire_type"),
          -ends_with("TEXT")) %>% 
  mutate_all(as_factor) %>% 
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$desireType.pre_calc <-
  df %>%
  select(starts_with("desire_context"),
          -ends_with("TEXT")) %>% 
  mutate_all(as_factor) %>% 
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$nonDutchType.pre_calc <-
  df %>%
  select(starts_with("NonDutchType"),
          -ends_with("TEXT")) %>% 
  mutate_all(as_factor) %>% 
  unite(.,
        "Comb",
        sep = ", ",
        remove = TRUE,
        na.rm = TRUE) %>%
  pull

df$autonomySat.pre_calc <-
  psych::scoreItems(
    keys = c(1, 1, 1, 1),
    items = df %>% select(matches("^SDT0[1-4].pre")),
    min = 1,
    max = 7
  )$scores %>% 
  as.numeric
df$autonomyFrust.pre_calc <-
  psych::scoreItems(
    keys = c(1, 1, 1, 1),
    items = df %>% select(matches("^SDT0[5-8].pre")),
    min = 1,
    max = 7
  )$scores %>% 
  as.numeric

df$relatednessSat.pre_calc <-
  psych::scoreItems(
    keys = c(1, 1, 1, 1),
    items = df %>% select(matches("^SDT(09|1[0-2]).pre")),
    min = 1,
    max = 7
  )$scores %>% 
  as.numeric
df$relatednessFrust.pre_calc <-
  psych::scoreItems(
    keys = c(1, 1, 1, 1),
    items = df %>% select(matches("^SDT1[3-6].pre")),
    min = 1,
    max = 7
  )$scores %>% 
  as.numeric

df$competenceSat.pre_calc <-
  psych::scoreItems(
    keys = c(1, 1, 1, 1),
    items = df %>% select(matches("^SDT(1[7-9]|20).pre")),
    min = 1,
    max = 7
  )$scores %>% 
  as.numeric
df$competenceFrust.pre_calc <-
  psych::scoreItems(
    keys = c(1, 1, 1, 1),
    items = df %>% select(matches("^SDT2[1-4].pre")),
    min = 1,
    max = 7
  )$scores %>% 
  as.numeric

df$IntGrAnx.pre_calc <-
  psych::scoreItems(
    keys = c(rep(1,6),rep(-1,6)),
    items = df %>% select(matches("^IntGrAnx[0-9]{2}.?\\.pre")),
    min = 1,
    max = 10
  )$scores %>% 
  as.numeric

df$swl.pre_calc <-
  psych::scoreItems(
    keys = rep(1,5),
    items = df %>% select(matches("^SWL[0-9]{2}\\.pre")),
    min = 1,
    max = 7,
    missing = TRUE,
    impute = "none",
  )$scores %>% 
  as.numeric

df$mdmq.alertness.pre_calc <- 
  psych::scoreItems(
    keys = c(1, -1, -1, 1),
    items = df %>% select(MDMQ02.pre, MDMQ05.pre, MDMQ07.pre, MDMQ10.pre),
    min = 1,
    max = 6,
    missing = TRUE,
    impute = "none",
  )$scores %>% 
  as.numeric
df$mdmq.calmness.pre_calc <- 
  psych::scoreItems(
    keys = c(-1, 1, -1, 1),
    items = df %>% select(MDMQ03.pre, MDMQ06.pre, MDMQ09.pre, MDMQ12.pre),
    min = 1,
    max = 6,
    missing = TRUE,
    impute = "none",
  )$scores %>% 
  as.numeric
df$mdmq.valence.pre_calc <- 
  psych::scoreItems(
    keys = c(1, -1, 1, -1),
    items = df %>% select(MDMQ01.pre, MDMQ04.pre, MDMQ08.pre, MDMQ11.pre),
    min = 1,
    max = 6,
    missing = TRUE,
    impute = "none",
  )$scores %>% 
  as.numeric

df$IntGrAnx.post_calc <-
  psych::scoreItems(
    keys = c(rep(1,6),rep(-1,6)),
    items = df %>% select(matches("^IntGrAnx[0-9]{2}.?\\.post")),
    min = 1,
    max = 10
  )$scores %>% 
  as.numeric

df$swl.post_calc <-
  psych::scoreItems(
    keys = rep(1,5),
    items = df %>% select(matches("^SWL[0-9]{2}\\.post")),
    min = 1,
    max = 7,
    missing = TRUE,
    impute = "none",
  )$scores %>% 
  as.numeric

varNamIndicesS1 <-
  append(varNamIndicesS1,
         df %>% select(ends_with("_calc")) %>% names)

@@

1.  We first create person, survey type, and measurement ID variables.\
2.  We then created indices of scales. Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).\
3.  We add information about the interaction partner to the beep during which a person was selected as an interaction partner.\
4.  We cluster mean-center key variables within participants.\
5.  Finally, we calculated several basic participant summaries (averages across all measurement occasions).

@@

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("relatednessSelf", "relatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$relatednessInteraction <- rowMeans(df[c("relatednessSelf", "relatednessOther")], na.rm = TRUE)
df$relatednessInteraction[df$relatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; JK: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$relatedness <-
  rowMeans(df[, c("relatednessInteraction", "relatednessNoInteraction")],
           na.rm = TRUE) %>%
  ifelse(is.nan(.), NA, .)

@@

1.  We first create person, survey type, and measurement ID variables.\
2.  We then created indices of scales. Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).\
3.  We cluster mean-center key variables within participants.\
4.  Finally, we calculated several basic participant summaries (averages across all measurement occasions).

@@

::: {.alert .alert-info .alert-dismissible .fade .in role="alert"}
<a class="close" data-dismiss="alert" aria-label="close">×</a> <i class="fas fa-info-circle"></i> <b>Note: </b><br/> This needs to be adjusted current missingness criterion set to more conservative 33%.
:::

@@

```{r testOptimizer05}
cleanM <- function(M, c = 55) {
  check <- list()
  rowNamesOut <- c()
  colNamesOut <- c()
  for (i in 1:length(c(row.names(M), names(M)))) {
    rowMeans <- rowMeans(M) * 100
    colMeans <- colMeans(M) * 100
    rcMeans <- c(rowMeans, colMeans)
    rm <- which.min(rcMeans) %>% names
    rc <- ifelse(startsWith(rm, "PP_"), "row", "col")

@@

dtS1RedInfo <- cleanM(M = as.data.frame(dtS1Availability), c = 55)

@@

```{r s2SampleReduction}
dtS2RedInfo <- cleanM(M = as.data.frame(dtS2Availability), c = 55)

@@

# remove glitch entries 
dtS2Red <- dtS2Red[!(dtS2Red$PID == 46 & dtS2Red$TIDnum == 57 & dtS2Red$ended == "2018-12-20 21:58:31"),]
dtS2Red <- dtS2Red[!(dtS2Red$PID == 46 & dtS2Red$TIDnum == 59 & dtS2Red$ended == "2018-12-20 21:58:31"),]

@@

```{r s3SampleReduction}
dtS3RedInfo <- cleanM(M = as.data.frame(dtS3Availability), c = 55)

@@

We ultimately aim to create 20 imputed data sets to perform the analyses on. As outlined by @Monden2015, we will use the key variables themselves as well as auxiliary variables to impute missing values. Auxiliary variables are any pre-, post-, or daily dairy variables other than the main variables. If there are any modeling issues we will limit the auxiliary variables to all variables that that are significantly ($p$ \< .01) and meaningfully ($r$ \> .3) correlated with (1) the key variables or (2) missingness on the key variables.

We create the imputed data set for each of the analyses. This includes the main analyses with across all three studies, using the set of common variables, as well as follow-up analyses for study-specific, interaction-specific and time scale specific data sets.

```{r varNames}
varNamS123Aux <- varNames %>%
  filter(
    aux != 0,
    studyS1 == "S1",
    studyS2 == "S2",
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull
varNamS1Aux <- varNames %>%
  filter(
    aux != 0,
    studyS1 == "S1"
  ) %>%
  select(varNam) %>%
  pull
varNamS2Aux <- varNames %>%
  filter(
    aux != 0,
    studyS2 == "S2"
  ) %>%
  select(varNam) %>%
  pull
varNamS3Aux <- varNames %>%
  filter(
    aux != 0,
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull

varNamS123PCA <- varNames %>%
  filter(
    pca != 0,
    studyS1 == "S1",
    studyS2 == "S2",
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull
varNamS1PCA <- varNames %>%
  filter(
    pca != 0,
    studyS1 == "S1"
  ) %>%
  select(varNam) %>%
  pull
varNamS2PCA <- varNames %>%
  filter(
    pca != 0,
    studyS2 == "S2"
  ) %>%
  select(varNam) %>% 
  pull
varNamS3PCA <- varNames %>%
  filter(
    pca != 0,
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull

varNamOut <- c(
  "ResponseId",
  "relatednessNoInteraction",
  "relatednessSelf",
  "relatednessOther",
  "autonomy_Int",
  "autonomy_NoInt",
  "competence_Int",
  "competence_NoInt",
  varNamS1PCA[grepl('^MDMQ', varNamS1PCA)],
  varNamS2PCA[grepl('^ProSo|^AntiSo', varNamS2PCA)],
  varNamS3PCA[grepl(
    '^ProSo|^AntiSo|^agency|^autoFrust|^autoSat|^relatFrust|^relatSat|^compFrust|^compSat|^lonely[0-9]|^emotRegPos|^emotRegNeg',
    varNamS3PCA
  )]
)
varNamCore <- c(
  "PID",
  "TID",
  "TIDnum"
)
varNamNewS1 <- c(
  "relatedness",
  "autonomy",
  "competence",
  "alertness", 
  "calmness", 
  "valence"
)
varNamNewS2 <- c(
  "relatedness",
  "autonomy",
  "competence",
  "ProSo", 
  "AntiSo"
)
varNamNewS3 <- c(
  "relatedness",
  "autonomy",
  "competence",
  "ProSo", 
  "AntiSo",
  "agency",
  "autoFrust",
  "autoSat",
  "relatFrust",
  "relatSat",
  "compFrust",
  "compSat",
  "lonely",
  "emotRegPos",
  "emotRegNeg"
)

varNamNewCat <- c(
  "closeness_Calc",
  "gender_Calc",
  "ethnicity_Calc",
  "relationship_Calc"
)

varNamIntDep <- c(
  varNamS123PCA[grepl('^InteractionContext|AttitudesPartner|KeyNeedDueToPartner|^quality', varNamS123PCA)]
)

varNamIndiceItemsS1 <- varNames %>%
  filter(
    aux == -1,
    studyS1 == "S1"
  ) %>%
  select(varNam) %>%
  pull %>%
  append(., gsub(".pre|.post|_calc", "", varNamIndicesS1)) %>%
  unique

varNamS123MI <- c(varNamCore, varNamS123Aux)
varNamS1MI <- c(varNamCore, varNamIndicesS1, varNamS1Aux[!varNamS1Aux %in% varNamIndiceItemsS1]) #
varNamS2MI <- c(varNamCore, varNamNewS2, varNamS2Aux)
varNamS3MI <- c(varNamCore, varNamNewS3, varNamS3Aux)

varNamS123PCA <- c(varNamCore, varNamS123PCA[!varNamS123PCA %in% varNamOut])
varNamS1PCA <- c(varNamCore, varNamNewS1, varNamS1PCA[!varNamS1PCA %in% varNamOut])
varNamS2PCA <- c(varNamCore, varNamNewS2, varNamS2PCA[!varNamS2PCA %in% varNamOut])
varNamS3PCA <- c(varNamCore, varNamNewS3, varNamS3PCA[!varNamS3PCA %in% varNamOut])

@@

```{r MiMain}

varNamS123MIPsbl <- c(
  paste(varNamS123MI, rep(".pre", length(varNamS123MI)), sep = ""),
  varNamS123MI,
  paste(varNamS123MI, rep(".post", length(varNamS123MI)), sep = "")
)

varNamS123MiRed <- Reduce(
  intersect,
  list(
    dtS1Red %>% select(PID, TID, TIDnum, any_of(varNamS123MIPsbl)) %>% names,
    dtS2Red %>% select(PID, TID, TIDnum, any_of(varNamS123MIPsbl)) %>% names,
    dtS3Red %>% select(PID, TID, TIDnum, any_of(varNamS123MIPsbl)) %>% names
  )
)

@@

```{r MiS1Prep}
varNamS1MiPsbl <- c(
  paste(varNamS1MI, rep(".pre", length(varNamS1MI)), sep = ""),
  varNamS1MI,
  paste(varNamS1MI, rep(".post", length(varNamS1MI)), sep = "")
)

@@

dtMiS1 <- dtS1Red %>% 
  select(TID, any_of(varNamS1MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame
